NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-06-02 ms_nihao_budget.tex
add a unit in the conclusion of figure 3

{\bf In Fig.~\ref{fig:inout}, we calculate the fractions of gas (in each phase)
inside the virial radius (blue points) and between 
the virial and baryon radii (red points).
%
The upper-left panel shows the  fractions of cold gas. The fractions
of cold gas between the virial radius and baryon radius of galaxies with
halo masses in the range between $10^{9} \Msun$ to  $10^{10} \Msun$
are greater than 80\%. As the halo mass increases, this fraction goes
down dramatically, in the mass range between $10^{10} \Msun$ and
$10^{11} \Msun$ the fractions are less than  20\% for most of galaxies
and the fractions for galaxies with halo mass above $10^{11} \Msun$ are
almost 0.  For the cold gas inside the virial radius, the fractions
increase gradually as halo mass increases and the maximum fraction is
about 20\% with at a halo mass of $10^{12} \Msun$.
%
The upper-right panel shows the fractions of cool gas.  The fractions
of cool gas in region outside of virial radius  increase from 0 at
halo masses are $10^9 \Msun$ to 80\% at halo  masses are around
$10^{10} \Msun$ to $10^{11} \Msun$, then  decrease in higher mass
range and reach 0 again at halo masses are $10^{12} \Msun$. The cool
gas inside virial radius shares  a similar trend but the maximum
fraction is about 40\% at  halo masses are $10^{11} \Msun$.
%
The fractions for warm-hot gas are shown in the lower-left panel.
The trends of the gas inside and outside gas are quite similar
which increase as the halo masses increase monotonically and whose 
maximum values are only 20\%.
%
The hot gas shown in the lower-right panel and is negligible both
inside and outside the virial radius across the whole mass range we
study.
%
We thus conclude that, for galaxies with halo mass 
below $10^{11}$, the majority of baryons associated with the
dark matter halo are in the cold and cool phases, 
and are located well outside of virial radius. For the gas inside
virial radius, the majority is cool gas for the galaxies with
halo masses are $10^{11} \Msun$ and when halo masses are higher
than $10^{11} \Msun$ the fractions of cold gas, cool gas and 
warm-hot gas are comparable.}

>>>>

{\bf In Fig.~\ref{fig:inout}, we calculate the fractions of gas (in each phase)
inside the virial radius (blue points) and between 
the virial and baryon radii (red points).
%
The upper-left panel shows the  fractions of cold gas. The fractions
of cold gas between the virial radius and baryon radius of galaxies with
halo masses in the range between $10^{9} \Msun$ to  $10^{10} \Msun$
are greater than 80\%. As the halo mass increases, this fraction goes
down dramatically, in the mass range between $10^{10} \Msun$ and
$10^{11} \Msun$ the fractions are less than  20\% for most of galaxies
and the fractions for galaxies with halo mass above $10^{11} \Msun$ are
almost 0.  For the cold gas inside the virial radius, the fractions
increase gradually as halo mass increases and the maximum fraction is
about 20\% with at a halo mass of $10^{12} \Msun$.
%
The upper-right panel shows the fractions of cool gas.  The fractions
of cool gas in region outside of virial radius  increase from 0 at
halo masses are $10^9 \Msun$ to 80\% at halo  masses are around
$10^{10} \Msun$ to $10^{11} \Msun$, then  decrease in higher mass
range and reach 0 again at halo masses are $10^{12} \Msun$. The cool
gas inside virial radius shares  a similar trend but the maximum
fraction is about 40\% at  halo masses are $10^{11} \Msun$.
%
The fractions for warm-hot gas are shown in the lower-left panel.
The trends of the gas inside and outside gas are quite similar
which increase as the halo masses increase monotonically and whose 
maximum values are only 20\%.
%
The hot gas shown in the lower-right panel and is negligible both
inside and outside the virial radius across the whole mass range we
study.
%
We thus conclude that, for galaxies with halo mass 
below $10^{11} \Msun$, the majority of baryons associated with the
dark matter halo are in the cold and cool phases, 
and are located well outside of virial radius. For the gas inside
virial radius, the majority is cool gas for the galaxies with
halo masses are $10^{11} \Msun$ and when halo masses are higher
than $10^{11} \Msun$ the fractions of cold gas, cool gas and 
warm-hot gas are comparable.}
